### 2022-05-16 manuscript.Rmd
manuscript

---
title: "Accuracy of Thoughts, Affect, and Personality impressions"
author: "Murat Kezer"
output: 
    html_document:
      theme: cerulean
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 3
      code_folding: hide
---

```{r include=F}
knitr::opts_chunk$set(echo = TRUE, 
                      tidy = TRUE, 
                      cache = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

options(scipen = 999)
```

```{r message = FALSE, results = 'hide'}
library(fs)
library(here)
library(rio)
library(tidyverse)
library(magrittr)
```

# Import data
```{r}
paths <- dir_ls(here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

walk2(df_names, paths, ~{
  assign(.x, import(.y), envir = .GlobalEnv)
})
```

# Make variable types/names congruent for merging
```{r}
# rename
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

old_names <- names(raw_informant_data[,44:189])
new_names <- paste0(names(raw_informant_data[, 44:189]), "_inf")

raw_informant_data %<>% 
  rename_at(vars(old_names), ~ new_names)

# remove
ind_diffs_self %<>% 
  select(-sex:-strait26,
         -Perceiver, -Target)

raw_informant_data %<>% 
  select(-Perceiver,
         -name:-V3)

# bfi
informant_bfi <- 
  raw_informant_data %>% 
  select(PerUn, starts_with("bfi")) %>% 
    group_by(PerUn) %>% 
    summarise(across(bfi1:bfi26, 
                     mean, na.rm = TRUE)
              ) %>% 
    ungroup() %>% 
    rename_at(vars(bfi1:bfi26), ~ paste0("itrait", 1:26)
              )
```

# Merge
```{r}
df <- list(perceiver_target_data,
           perceiver_target_affect_EA,
           ind_diffs_self,
           informant_bfi,
           aggregated_informant_data) %>% 
  reduce(left_join)

rm(list = gdata::keep(df))
```

# Clean and rename variables
```{r}

source("functions.R")

```

### 2022-05-16 manuscript.Rmd
clean up manuscript

@@
 ```{r message = FALSE, results = 'hide'}
-library(fs)
-library(here)
-library(rio)
 library(tidyverse)
-library(magrittr)
 ```
-
-# Import data
-```{r}
-paths <- dir_ls(here("data"))
-df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)
-
-walk2(df_names, paths, ~{
-  assign(.x, import(.y), envir = .GlobalEnv)
-})
-```
-
-# Make variable types/names congruent for merging
-```{r}
-# rename
-ind_diffs_self %<>% 
-  rename(PerUn = SubNum)
-
-old_names <- names(raw_informant_data[,44:189])
-new_names <- paste0(names(raw_informant_data[, 44:189]), "_inf")
-
-raw_informant_data %<>% 
-  rename_at(vars(old_names), ~ new_names)
-
-# remove
-ind_diffs_self %<>% 
-  select(-sex:-strait26,
-         -Perceiver, -Target)
-
-raw_informant_data %<>% 
-  select(-Perceiver,
-         -name:-V3)
-
-# bfi
-informant_bfi <- 
-  raw_informant_data %>% 
-  select(PerUn, starts_with("bfi")) %>% 
-    group_by(PerUn) %>% 
-    summarise(across(bfi1:bfi26, 
-                     mean, na.rm = TRUE)
-              ) %>% 
-    ungroup() %>% 
-    rename_at(vars(bfi1:bfi26), ~ paste0("itrait", 1:26)
-              )
-```
-
-# Merge
-```{r}
-df <- list(perceiver_target_data,
-           perceiver_target_affect_EA,
-           ind_diffs_self,
-           informant_bfi,
-           aggregated_informant_data) %>% 
-  reduce(left_join)
-
-rm(list = gdata::keep(df))
-```
-
-# Clean and rename variables
-```{r}
-
-source("functions.R")
-
-```

### 2022-05-16 manuscript.Rmd
Titles and intro

@@
 
-```{r message = FALSE, results = 'hide'}
+```{r message=FALSE, include=FALSE, results='hide'}
 library(tidyverse)
 ```
+
+# Introduction
+  As the saying goes, “it takes two to tango,” and interpersonal perception might be considered the social-cognitive equivalent of such a complex dance between perceivers (who make interpersonal judgments) and targets (who are judged).
+Even very brief interpersonal interactions are rich exchanges where targets emit behavior and cues via numerous channels.
+Thus it follows that perceivers can and do form perceptions on a range of dimensions, varying from fleeting judgments about discrete and context-specific thoughts or feelings, to snapshot judgments that regard more global and enduring characteristics.
+For example, empathic accuracy researchers examine the accuracy of perceivers’ judgments of targets’ specific thoughts and feelings (Ickes, Stinson, Bissonette, & Garcia, 1990) or changes in ongoing affective states (Levenson & Ruef, 1992).
+Personality researchers examine the accuracy of perceivers’ judgments of targets’ traits (Funder & Colvin, 1997), as well as the accuracy of perceptions about how others judge one’s own traits (i.e., meta-perceptions; Kenny & DePaulo, 1993).
+
+# Method
+## Participants
+
+## Measures
+
+## Procedure
+
+## Analytical strategy
+
+# Results

### 2022-05-16 manuscript.Rmd
finish intro

@@
 ---
-title: "Accuracy of Thoughts, Affect, and Personality impressions"
+title: "Target Readability in Interpersonal Accuracy"
 author: "Murat Kezer"
@@
 
+  Common sense suggests that navigating our complex social environment requires at least a basic competency at making accurate judgments of others as well as making oneself readable to others.
+However, one common theme across domains of interpersonal perception research has been a disproportionate focus on perceivers, emphasizing traits, motivations, and biases that allow perceivers to accurately understand targets (for reviews
+see Davis & Kraus, 1997; Hall & Bernieri, 2001).
+This one-sided focus has come at the expense of understanding the role targets play in these processes.
+Making the inevitable comparison to reading a passage of text, we know much more about the reader than we do about the book.
+The imbalance is striking given that interpersonal perception is inherently dyadic – a perceiver cannot make a judgment without a target person to judge.
+The overarching goal of this project is to address this imbalance and explore what makes for more or less “readable” targets.
+
+  According to Funder’s (1995) Realistic Accuracy Model, accurate interpersonal perceptions can be facilitated by good judges, but also by good targets.Funder further proposed that accurate perceptions are a product of a series of stages.
+A target must emit some relevant behavior that is made available to the perceiver.
+The perceiver must then detect these cues and correctly utilize them to make a judgment.
+Note that RAM is not a general process model of how all interpersonal judgments are formed, but rather a description of how accurate judgments are formed.
+The target’s direct role in
+this process will be most important in the first two stages (relevance and availability).
+Characteristics that make targets more likely to emit relevant cues and enhance the availability of those cues are likely to be correlated with readability.
+The present study focuses on three groups of predictors of target readability: Expressivity, social-threat sensitivity and psychological adjustment.
+
+  Even though studies suggest that the good target seems to be a more plausible determinate of interpersonal accuracy than the good judge, we still know much less about which targets are more readable than others and whether
+or not target readability is a general trait or if it is instead specific to different types of judgments.
+The goal of this project is to address this imbalance.
+Because looking for more or less readable targets presumes individual differences in readability, Aim 1 is to examine how variance in interpersonal accuracy is distributed across levels (i.e., how variance associated with differences among targets compares to variance associated with differences among perceivers).
+Aim 2 is to examine whether target readability correlates across measures (e.g., whether a target whose personality traits are easy to read also has affect that is easy read) by using multiple accuracy measures that represent a range of interpersonal judgments.
+To capture a more complete picture of the complexity of interpersonal processes, the dimensions targets were judged on ranged from stable (i.e., personality traits) to dynamic (i.e., continuous affect and discrete thoughts that potentially change moment by moment).
+And finally Aim 3 is to explore the individual differences (assessing the constructs described above) that may correlate with target readability and look for patterns of interrelations across outcome measures.
+
+  In order to test these research aims, participants were videotaped interacting with a partner during brief “getting-acquainted” conversations using a round-robin design where each person served as perceiver and target in multiple interactions.
+After interacting, people rated their partner’s personality traits, and dynamically changing affect and thoughts.
+In order to assess accuracy, each partner made parallel ratings about their own traits, affect, and thoughts.
+Measures of expressivity, social-threat sensitivity,
+and psychological adjustment were collected at a later time point from the participants as well as informants in order to examine whether these variables were related to target readability on traits, affect, and thoughts.
+
 # Method
 ## Participants
+Undergraduates from the University of Oregon participated in this study in
+exchange for course credit.
+In total, 53 groups of four participated in this study, which resulted in a total of 212 participants (63.7% women; Mage = 20.17, SDage = 2.99; 68.4% Caucasian, 11.8% Asian, 5.7% Black, 5.7% Hispanic, 8.4% other or missing).
+Participants were asked not to sign up for the study with friends so the partners were generally unacquainted.
 
@@
 # Results
+
+# Discussion
+
+# Author Note
+"This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."

### 2022-05-16 manuscript.Rmd
participants
method
participants, measures, procedure, and analytical plan

@@
         collapsed: FALSE
-      toc_depth: 3
+      toc_depth: 2
       code_folding: hide
@@
   Common sense suggests that navigating our complex social environment requires at least a basic competency at making accurate judgments of others as well as making oneself readable to others.
-However, one common theme across domains of interpersonal perception research has been a disproportionate focus on perceivers, emphasizing traits, motivations, and biases that allow perceivers to accurately understand targets (for reviews
-see Davis & Kraus, 1997; Hall & Bernieri, 2001).
+However, one common theme across domains of interpersonal perception research has been a disproportionate focus on perceivers, emphasizing traits, motivations, and biases that allow perceivers to accurately understand targets (for reviews see Davis & Kraus, 1997; Hall & Bernieri, 2001).
 This one-sided focus has come at the expense of understanding the role targets play in these processes.
@@
 Note that RAM is not a general process model of how all interpersonal judgments are formed, but rather a description of how accurate judgments are formed.
-The target’s direct role in
-this process will be most important in the first two stages (relevance and availability).
+The target’s direct role in this process will be most important in the first two stages (relevance and availability).
 Characteristics that make targets more likely to emit relevant cues and enhance the availability of those cues are likely to be correlated with readability.
@@
 
-  Even though studies suggest that the good target seems to be a more plausible determinate of interpersonal accuracy than the good judge, we still know much less about which targets are more readable than others and whether
-or not target readability is a general trait or if it is instead specific to different types of judgments.
+  Even though studies suggest that the good target seems to be a more plausible determinate of interpersonal accuracy than the good judge, we still know much less about which targets are more readable than others and whether or not target readability is a general trait or if it is instead specific to different types of judgments.
 The goal of this project is to address this imbalance.
@@
 In order to assess accuracy, each partner made parallel ratings about their own traits, affect, and thoughts.
-Measures of expressivity, social-threat sensitivity,
-and psychological adjustment were collected at a later time point from the participants as well as informants in order to examine whether these variables were related to target readability on traits, affect, and thoughts.
+Measures of expressivity, social-threat sensitivity, and psychological adjustment were collected at a later time point from the participants as well as informants in order to examine whether these variables were related to target readability on traits, affect, and thoughts.
 
-# Method
+# Method {.tabset .tabset-fade}
 ## Participants
-Undergraduates from the University of Oregon participated in this study in
-exchange for course credit.
+Undergraduates from the University of Oregon participated in this study in exchange for course credit.
 In total, 53 groups of four participated in this study, which resulted in a total of 212 participants (63.7% women; Mage = 20.17, SDage = 2.99; 68.4% Caucasian, 11.8% Asian, 5.7% Black, 5.7% Hispanic, 8.4% other or missing).
@@
 ## Measures
+### Trait judgments
+
+Participants rated their own and their partners’ personality trait ratings using a 21-item shortened version of the Big Five Inventory (BFI; John & Srivastava, 1999) using a 7-point Likert scale (1 = strongly disagree, 7 = strongly agree).
+Three additional items were included to assess intelligence (e.g., “Receives very good grades”).
+Two additional items were included to assess honesty (e.g., “Is trustworthy”).
+
+### Affect judgments
+
+In the target phase, participants reported their moment-by-moment affect following established procedures (Zaki et al., 2008) for the first two minutes of each video.
+To do this, participants watched each video and continuously rated the level of positive to negative affect they remember feeling at each moment using a sliding 9-point scale (1 = very negative, 9 = very positive) that was presented onscreen immediately below the video clip.
+Participants were instructed to use their mouse to “rate how you felt at each moment” and adjust the sliding scale as often as necessary.
+The computer recorded 10 samples per second that were averaged to provide a single affect rating for each second.
+In the perceiver phase, participants rated their partner’s moment-by-moment affect for the first two minutes of each video.
+
+### Thought judgments
+
+In the target phase, participants were asked to report the specific discrete, dynamic thoughts they remember having when the interaction took place following the Ickes methodology for assessing empathic accuracy for thoughts (Ickes et al., 1990).
+To ensure an adequate number of thoughts were reported, the videos were stopped at five pre-determined times (2:00, 2:45, 3:30, 4:15, 5:00) as opposed to freely allowing participants to indicate when they remembered having had a thought (see Verhofstadt, Buysse, Ickes, Davis, & Devoldre, 2008 for a similar variation on the original empathic accuracy paradigm).
+In the perceiver phase, participants were asked to
+guess their partner’s specific thoughts at each of the pre-determined tape stops.
+To code perceivers’ accuracy for targets’ specific thoughts, independent raters compared each participant’s inference to the actual thought reported by the target.
+The inferences were coded for accuracy using a 4-point scale (0 = essentially different content, 1 = somewhat correct content, but something notable is missing or incorrect, 2 = mostly correct content, but some small element is missing or incorrect, and 3 = essentially the same content).
+The coding was split into four batches and four to five
+independent raters coded each batch.
+The raters were reliable (Cronbach’s alpha ranges .91 to .92) thus accuracy ratings were averaged across raters for each inference and rescaled to yield a scale ranging from 0 (zero accuracy) to 100 (complete accuracy).
+
+### Thought judgment baseline accuracy scores
+
+Also following Ickes et al.
+(1990), we estimated baseline accuracy for perceivers’ thought judgments.
+Baseline accuracy refers to the overlap between the content of perceivers’ inferences and targets’ thoughts that is due to general knowledge (of a target or of the whole target pool), rather than distinctive knowledge of one specific thought.
+To estimate between-target baseline accuracy, three inferences were randomly selected for each perceiver from each target they interacted with.
+Each inference was then paired with different randomly selected thoughts reported by different targets from different groups.
+These pairings were rated for accuracy (using the same 4-point scale as above) by three judges.
+Accuracy ratings for
+each inference were averaged across judges (Cronbach’s α = .64).
+
+### Expressivity
+
+Participants completed the following measures of constructs related to expressivity: the Masking Scale (13 items; Gross & John, 1998), the Berkeley Expressivity Questionnaire (16 items; Gross & John, 1995), and the Emotion Regulation Questionnaire (10 items; Gross & John, 2003).
+The BEQ is comprised of three subscales that assess positive expressivity, negative expressivity, and impulse strength.
+The ERQ is comprised of two subscales that assess two types of emotion regulation, expressive suppression and cognitive reappraisal, although only the expressive suppression subscale was of interest as a potential correlate of readability.
+The Extraversion subscale of the Big Five Inventory (BFI; John & Srivastava, 1999) which was used to assess trait judgments (see description below) was also computed as a potential component of expressivity that might relate to target readability.
+
+### Social-threat sensitivity
+
+Participants completed the following measures of constructs related to social-threat sensitivity: the Need to Belong Scale (10 items; Leary, Kelly, Cottrell, & Schreindorfer, 2005), the UCLA Loneliness Scale (20 items; Russell, 1996), and the Fear of Negative Evaluation Scale (12 items; Leary, 1983).
+Participants completed the Social Interaction Anxiety Scale (6 items; Peters, Sunderland, Andrews, Rapee, & Mattick, 2012) which is comprised of two subscales that assess social anxiety and social phobia.
+Participants completed the Attachment Style Measure (13 items; Simpson, 1990) which is comprised of three subscales that assess the three prototypical types of attachment: secure, anxious, and avoidant (note that these are not categorical and treated continuously).
+In keeping with the direction of the other two subscales, the items comprising the secure attachment subscale were coded such that higher values indicate less secure attachment.
+
+### Psychological adjustment
+
+Participants completed the following measures of constructs related to psychological adjustment: the Authenticity Scale (12 items; Wood, Linley, Maltby, Baliousis, & Joseph, 2008), the Rosenberg Self-Esteem Scale (10 items; Rosenberg, 1965), the Satisfaction with Life Scale (5 items; Diener, Emmons, Larsen, & Griffin, 1985), and the Sense of Power Scale (8 items; Anderson, John, & Keltner, 2012).
 
 ## Procedure
+### Phase I
+
+For the getting-acquainted task, participants interacted with each other in pairs.
+The pairs were instructed that their goal was to get to know one another as best they could in five minutes.
+To encourage more engaging conversations and ensure discussions went beyond perfunctory questions like “Where are you from?” and “What classes are you taking?”, each pair was provided with an envelope that contained slips of paper with a number of possible discussion questions.
+Participants were told that their goal was not to cover as many questions as possible in 5 minutes, but rather to explore each other’s responses to one question in depth.
+The discussion questions were drawn from the pool of items in the Aron, Melinat, Aron, Vallone, and Bator (1997) Closeness Generating Exercise, as well as similar items written for this study or drawn from conversation-starter board games such as Table Topics®.
+Representative items include questions such as; “For what in your life do you feel most grateful?”, “If you could change anything about the way you were raised, what would it be?”, and “If you could go back in time 5 years, what piece of advice would you give your younger self?” (see Appendix B for a list of all possible discussion questions).
+Items were selected so that answers required some self-disclosure, but not so much that it would make participants overly uncomfortable to discuss with someone they did not know well.
+Immediately after each interaction participants were separated and asked to rate their partners’ personality traits (see details below) as well as a number of items assessing dyadic rapport (see details below).
+Participants completed this procedure three times until all participants had interacted with and rated every other participant in the group.
+The experiment presentation software, MediaLab (Jarvis, 2012) was used to collect all measures in the lab session.
+
+### Phase II
+
+After all possible dyads had interacted, everyone in the group was separated to private cubicles that were each equipped with a computer and headphones.
+Participants (now acting as targets) watched each of the three videos of the dyadic interactions they participated in.
+For the first two minutes of each video, participants were asked to report their moment-by-moment affect (see details below).
+At the end of the first two minutes and at the end of each 45 second period thereafter, the video was paused and participants were asked to report the specific thoughts they remembered having at that time (see details below).
+It was stressed that participants should report the affect and thoughts they remembered having experienced during the original interaction and not any affect or thoughts they experienced in reaction to viewing the videotapes.
+Next participants (now acting as perceivers) again watched each of the three videos of the dyadic interactions they participated in.
+However, this time they continuously rated the affect of their partner for the first two minutes of the video and inferred their partner’s thoughts at each of the pre-determined tape stops.
 
 ## Analytical strategy
+### Trait judgment
+Trait judgment accuracy was modeled using the Social Accuracy Model (SAM; Biesanz, 2010).
+SAM was developed for trait judgment research and is appropriate when perceivers make judgments of a target across some series of attributes (e.g., multiple personality trait items).
+SAM simultaneously models perceivers’ judgments as a function of the criterion measure (e.g., a specific target’s self-reported extraversion) and the mean for the criterion measure (e.g., the average level of self-reported extraversion).
+As a result, the raw profile relationship is decomposed into distinctive accuracy (the correspondence between perceivers’ judgments and targets’ self-reports controlling for the average person’s personality) and normative accuracy (the correspondence between perceivers judgments’ and the average person’s personality after controlling for targets’ self-reports).
+
+### Affect accuracy
+The continuous affect ratings were first binned (following Zaki et al., 2008) by calculating a non-moving average for each five-second interval.
+Each binned interval served as one data point.
+Affect accuracy was also modeled using SAM: perceivers’ affect judgments were predicted by targets’ actual affect ratings as well as average affect ratings.
+This is a novel application of SAM that has not yet been tested.
+However, because there may be a general affect trajectory that the modal dyadic interaction follows (e.g., people may start out feeling awkward but gradually warm to each other and thus affect follows a roughly upward linear trajectory), it is possible that affect accuracy could be broken down into normative and distinctive accuracy much like trait judgments.
+
+### Thought accuracy
+These data were modeled using the Social Relations Model (SRM; Kashy & Kenny, 1990; Kenny & LaVoie, 1985) which was developed for round-robin designs where interpersonal perceptions are measured.
+The SRM is also a cross-classified multilevel modeling strategy that breaks down a rating (in this case an accuracy score) as a function of the group mean, a perceiver effect, a target effect and a dyadic relationship effect.
+For example, Polly’s empathic accuracy for Tim is a function of their group mean3, the extent to which Polly is generally accurate at reading others’ thoughts, the extent to which Tim’s thoughts are generally accurately perceived by others, and Polly’s unique accuracy for Tim above and beyond the other main effects.
+Similar to decomposing overall accuracy into normative and distinctive components in the SAM analyses, baseline accuracy scores were calculated (see above for details) in order to estimate how much of the perceivers’ overall thought accuracy is attributable to making correct inferences based on general knowledge and/or stereotypes.
+Empathic accuracy scores were divided into normative (baseline accuracy) and distinctive accuracy (overall accuracy corrected for baseline accuracy) and SRM analyses were conducted on each component separately.
+
+To address Aim 1, baseline models with the above specified components were
+computed for each of the outcome measures.
+Using the R lme package (Bates, Maechler, Bolker, & Sarkar, 2013), the Empirical Bayes random target effect estimates for each of these models were extracted.
+These values were then used in the analyses addressing Aim 2 (determining whether target readability correlated across measures) and Aim 3 (determining whether individual differences predicted target readability).
 

### 2022-05-16 manuscript.Rmd
results
subheadings

@@
 
-# Results
+# Results {.tabset .tabset-fade}
+```{r, include = FALSE}
+# import functions
+source("functions.R")
+
+# import data
+df <- rio::import(here::here("data", "df.csv"))
+```
+
+## Descriptive statistics
+```{r}
+
+```
+Table 1 represents descriptive statistics for all the variables in the present study.
+
+```{r}
+table1
+```
+
+## Aim 1
+### Examine variance decomposition in interpersonal accuracy and compare across accuracy measures
+
+In order to decompose the variance in interpersonal accuracy and compare across accuracy measures I ran a series of baseline variance decomposition models on the accuracy measures.
+All analyses were conducted in R’s lme4 package (Bates et al., 2013).
+
+```{r}
+
+```
+
+## Aim 2
+### Examine interrelations among target readability estimates for different measures of interpersonal accuracy
+
+In order to examine interrelations among target readability estimates for different measures of interpersonal accuracy, the Empirical Bayes random target effect estimates were extracted from the analysis of the baseline models for each outcome measure (when target variance was nonzero).
+
+```{r}
+
+```
+
+## Aim 3
+### Investigate potential individual differences that correlate with target readability as well as look for patterns of individual differences that consistently correlate with readability across measures
+
+Based on guiding hypotheses generated from Funder’s RAM and previous research regarding target readability, individual differences linked to expressivity, social threat sensitivity, and psychological adjustment were measured.
+In order to investigate whether any of these measures correlated with target readability, I computed correlations between the Empirical Bayes random target effects extracted from the baseline models estimated in Aim 1 and the individual difference variables (assessed via self-reports and informant-reports).
+Table 8 displays these correlations separately for self-reports and informant-reports alongside 95% confidence intervals.
+
+```{r}
+
+```
 

### 2022-05-16 manuscript.Rmd
update intro
remove aims 2 and 3

@@
 Personality researchers examine the accuracy of perceivers’ judgments of targets’ traits (Funder & Colvin, 1997), as well as the accuracy of perceptions about how others judge one’s own traits (i.e., meta-perceptions; Kenny & DePaulo, 1993).
+Despite the numerous studies on interpersonal accuracy, to our knowledge, there is no study that investigated different types of interpersonal accuracy simultaneously.
+In other words, it is not clear whether interpersonal accuracy as well as components of accuracy (e.g., perceiver and target effects) for thoughts, affect, and personality traits are comparable.
 
-  Common sense suggests that navigating our complex social environment requires at least a basic competency at making accurate judgments of others as well as making oneself readable to others.
-However, one common theme across domains of interpersonal perception research has been a disproportionate focus on perceivers, emphasizing traits, motivations, and biases that allow perceivers to accurately understand targets (for reviews see Davis & Kraus, 1997; Hall & Bernieri, 2001).
-This one-sided focus has come at the expense of understanding the role targets play in these processes.
-Making the inevitable comparison to reading a passage of text, we know much more about the reader than we do about the book.
-The imbalance is striking given that interpersonal perception is inherently dyadic – a perceiver cannot make a judgment without a target person to judge.
-The overarching goal of this project is to address this imbalance and explore what makes for more or less “readable” targets.
-
-  According to Funder’s (1995) Realistic Accuracy Model, accurate interpersonal perceptions can be facilitated by good judges, but also by good targets.Funder further proposed that accurate perceptions are a product of a series of stages.
-A target must emit some relevant behavior that is made available to the perceiver.
-The perceiver must then detect these cues and correctly utilize them to make a judgment.
-Note that RAM is not a general process model of how all interpersonal judgments are formed, but rather a description of how accurate judgments are formed.
-The target’s direct role in this process will be most important in the first two stages (relevance and availability).
-Characteristics that make targets more likely to emit relevant cues and enhance the availability of those cues are likely to be correlated with readability.
-The present study focuses on three groups of predictors of target readability: Expressivity, social-threat sensitivity and psychological adjustment.
-
-  Even though studies suggest that the good target seems to be a more plausible determinate of interpersonal accuracy than the good judge, we still know much less about which targets are more readable than others and whether or not target readability is a general trait or if it is instead specific to different types of judgments.
-The goal of this project is to address this imbalance.
-Because looking for more or less readable targets presumes individual differences in readability, Aim 1 is to examine how variance in interpersonal accuracy is distributed across levels (i.e., how variance associated with differences among targets compares to variance associated with differences among perceivers).
-Aim 2 is to examine whether target readability correlates across measures (e.g., whether a target whose personality traits are easy to read also has affect that is easy read) by using multiple accuracy measures that represent a range of interpersonal judgments.
-To capture a more complete picture of the complexity of interpersonal processes, the dimensions targets were judged on ranged from stable (i.e., personality traits) to dynamic (i.e., continuous affect and discrete thoughts that potentially change moment by moment).
-And finally Aim 3 is to explore the individual differences (assessing the constructs described above) that may correlate with target readability and look for patterns of interrelations across outcome measures.
-
-  In order to test these research aims, participants were videotaped interacting with a partner during brief “getting-acquainted” conversations using a round-robin design where each person served as perceiver and target in multiple interactions.
+  In order to test this research question, participants were videotaped interacting with a partner during brief “getting-acquainted” conversations using a round-robin design where each person served as perceiver and target in multiple interactions.
 After interacting, people rated their partner’s personality traits, and dynamically changing affect and thoughts.
 In order to assess accuracy, each partner made parallel ratings about their own traits, affect, and thoughts.
-Measures of expressivity, social-threat sensitivity, and psychological adjustment were collected at a later time point from the participants as well as informants in order to examine whether these variables were related to target readability on traits, affect, and thoughts.
+Measures of expressivity, social-threat sensitivity, and psychological adjustment were also collected at a later time point from the participants in order to explore whether these variables are related to interpersonal accuracy traits, affect, and thoughts.
 
@@
 For example, Polly’s empathic accuracy for Tim is a function of their group mean3, the extent to which Polly is generally accurate at reading others’ thoughts, the extent to which Tim’s thoughts are generally accurately perceived by others, and Polly’s unique accuracy for Tim above and beyond the other main effects.
+
 Similar to decomposing overall accuracy into normative and distinctive components in the SAM analyses, baseline accuracy scores were calculated (see above for details) in order to estimate how much of the perceivers’ overall thought accuracy is attributable to making correct inferences based on general knowledge and/or stereotypes.
 Empathic accuracy scores were divided into normative (baseline accuracy) and distinctive accuracy (overall accuracy corrected for baseline accuracy) and SRM analyses were conducted on each component separately.
-
-To address Aim 1, baseline models with the above specified components were
-computed for each of the outcome measures.
-Using the R lme package (Bates, Maechler, Bolker, & Sarkar, 2013), the Empirical Bayes random target effect estimates for each of these models were extracted.
-These values were then used in the analyses addressing Aim 2 (determining whether target readability correlated across measures) and Aim 3 (determining whether individual differences predicted target readability).
 
@@
 ```{r}
+descriptive_df <-
+df %>% 
+  select(
+    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
+    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
+    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
+  )
+
+map_dbl(descriptive_df, mean, na.rm = TRUE)
+map_dbl(descriptive_df, sd, na.rm = TRUE)
+
+get_descrip(descriptive_df, Extr)
 
@@
 ```{r}
-table1
+
 ```
@@
 ```{r}
+# personality traits
+samdata <- import(here("data", "asd.csv"))
+
+library(lme4)
+library(lmerTest)
+options(digits=5)
+
+samdata$Avgtrait <- samdata$Avgtrait - 1
+
+samdata$targSRr <- samdata$targSR - samdata$Avgtrait
+
+samdata$targSRrC <- samdata$targSRr -0.0003679
+samdata$AvgtraitC <- samdata$Avgtrait - 4.0317762737
+samdata$ptraitC <- samdata$ptrait - 3.5820554
+
+null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
+summary (null1)
+
+samdat1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
+summary (samdat1)
+
+SAM1 <- lmer (ptrait ~ targSRrC + AvgtraitC + (targSRrC + AvgtraitC |PerUn) + (targSRrC + AvgtraitC |TarUn) + (targSRrC + AvgtraitC |DyUn), data=samdata)
+
+summary (SAM1)
+
+```
+
+```{r}
+# affect
+
+```
+
+```{r}
+# thought
 
@@
 In order to investigate whether any of these measures correlated with target readability, I computed correlations between the Empirical Bayes random target effects extracted from the baseline models estimated in Aim 1 and the individual difference variables (assessed via self-reports and informant-reports).
-Table 8 displays these correlations separately for self-reports and informant-reports alongside 95% confidence intervals.
+Table X displays these correlations separately for self-reports and informant-reports alongside 95% confidence intervals.
 

### 2022-05-16 manuscript.Rmd
update results section's structure

@@
 library(tidyverse)
+library(lme4)
+library(lmerTest)
 ```
@@
 
-## Descriptive statistics
+## Descriptive statistics for Empathic Accuracy
 ```{r}
@@
 
-## Aim 1
-### Examine variance decomposition in interpersonal accuracy and compare across accuracy measures
+## Interpersonal accuracy for thoughts, affect, and personality traits
 
@@
 # personality traits
-samdata <- import(here("data", "asd.csv"))
-
-library(lme4)
-library(lmerTest)
-options(digits=5)
-
-samdata$Avgtrait <- samdata$Avgtrait - 1
-
-samdata$targSRr <- samdata$targSR - samdata$Avgtrait
-
-samdata$targSRrC <- samdata$targSRr -0.0003679
-samdata$AvgtraitC <- samdata$Avgtrait - 4.0317762737
-samdata$ptraitC <- samdata$ptrait - 3.5820554
-
-null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
-summary (null1)
-
-samdat1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
-summary (samdat1)
+samdata <- import(here("data", "samdata.csv"))
 
@@
 
-## Aim 2
-### Examine interrelations among target readability estimates for different measures of interpersonal accuracy
-
-In order to examine interrelations among target readability estimates for different measures of interpersonal accuracy, the Empirical Bayes random target effect estimates were extracted from the analysis of the baseline models for each outcome measure (when target variance was nonzero).
+## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits
 
@@
 
-## Aim 3
-### Investigate potential individual differences that correlate with target readability as well as look for patterns of individual differences that consistently correlate with readability across measures
+```{r}
 
-Based on guiding hypotheses generated from Funder’s RAM and previous research regarding target readability, individual differences linked to expressivity, social threat sensitivity, and psychological adjustment were measured.
-In order to investigate whether any of these measures correlated with target readability, I computed correlations between the Empirical Bayes random target effects extracted from the baseline models estimated in Aim 1 and the individual difference variables (assessed via self-reports and informant-reports).
-Table X displays these correlations separately for self-reports and informant-reports alongside 95% confidence intervals.
+```
+
+```{r}
+
+```
+
+## Predictors of interpersonal accuracy
 

### 2022-05-16 manuscript.Rmd
descriptives and personality

@@
 
-map_dbl(descriptive_df, mean, na.rm = TRUE)
-map_dbl(descriptive_df, sd, na.rm = TRUE)
-
-get_descrip(descriptive_df, Extr)
-
+table1 <-
+tibble(
+  var = names(descriptive_df),
+  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
+  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
+)
 ```
@@
 ```{r}
-
+table1
 ```
 
-## Interpersonal accuracy for thoughts, affect, and personality traits
-
-In order to decompose the variance in interpersonal accuracy and compare across accuracy measures I ran a series of baseline variance decomposition models on the accuracy measures.
-All analyses were conducted in R’s lme4 package (Bates et al., 2013).
+## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits
 
 ```{r}
-# personality traits
-samdata <- import(here("data", "samdata.csv"))
+# personality
+samdata <- rio::import(here::here("data", "samdata.csv"))
 
-SAM1 <- lmer (ptrait ~ targSRrC + AvgtraitC + (targSRrC + AvgtraitC |PerUn) + (targSRrC + AvgtraitC |TarUn) + (targSRrC + AvgtraitC |DyUn), data=samdata)
+samdata <-
+  samdata %>% 
+  mutate(
 
-summary (SAM1)
+    Avgtrait = Avgtrait - 1,
+    targSRr = targSR - Avgtrait,
 
+    # Note to self: use a loop for these.
+    targSRrC = scale(targSRr, scale = FALSE, center = TRUE),
+    AvgtraitC = scale(Avgtrait, scale = FALSE, center = TRUE),
+    ptraitC = scale(ptrait, scale = FALSE, center = TRUE)
+  )
+
+## null model
+null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
+               data = samdata)
+
+sjPlot::tab_model(null1)
 ```
@@
 
-## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits
+## Interpersonal accuracy for thoughts, affect, and personality traits
+
+In order to decompose the variance in interpersonal accuracy and compare across accuracy measures I ran a series of baseline variance decomposition models on the accuracy measures.
+All analyses were conducted in R’s lme4 package (Bates et al., 2013).
 
 ```{r}
+# personality
+## final model
+SAM1 <- lmer(ptrait ~ targSRrC + AvgtraitC + 
+                (1 | PerUn) + 
+                (1 | TarUn) + 
+                (1 | DyUn), 
+              data = samdata)
+
+summary(SAM1)
+(SAM1)
+
+## fit a model for each perceiver
+models_dyad <- 
+samdata %>% 
+  group_by(PerUn) %>% 
+  nest() %>% 
+  mutate(models = map(data, ~ {
+
+    lm(ptrait ~ targSRrC + AvgtraitC, 
+              data = .x)
+
+  }
+                      )
+         )
+```
+
+```{r}
+# affect
 
@@
 ```{r}
-
-```
-
-```{r}
+# thought
 

### 2022-05-16 manuscript.Rmd
extract EB estimates and RE for personality

@@
 
-summary(SAM1)
-(SAM1)
+sjPlot::tab_model(SAM1)
+
+## save random effects
+lapply(ranef(SAM1), write.table, 
+       append = TRUE, 
+       file = "raneff from SAM1 for TRT.csv")
+
+## extract empirical bayesian estimates
+EBTRTtar <- ranef(SAM1)$TarUn
+colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
+EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
+summary(EBTRTtar)
+sapply(EBTRTtar,sd)
 

### 2022-05-16 manuscript.Rmd
move data merge to main and upload data for affect

--- 2022-05-16 manuscript.Rmd
@@
 
-# import data
-df <- rio::import(here::here("data", "df.csv"))
+# import data for exploratory predictors
+paths <- dir_ls(here("data"))
+df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)
+
+walk2(df_names, paths, ~{
+  assign(.x, import(.y), envir = .GlobalEnv)
+})
+
+# Make variable types/names congruent for merging
+# rename
+ind_diffs_self %<>% 
+  rename(PerUn = SubNum)
+
+old_names <- names(raw_informant_data[,44:189])
+new_names <- paste0(names(raw_informant_data[, 44:189]), "_inf")
+
+raw_informant_data %<>% 
+  rename_at(vars(old_names), ~ new_names)
+
+# remove
+ind_diffs_self %<>% 
+  select(-sex:-strait26,
+         -Perceiver, -Target)
+
+raw_informant_data %<>% 
+  select(-Perceiver,
+         -name:-V3)
+
+# bfi
+informant_bfi <- 
+  raw_informant_data %>% 
+  select(PerUn, starts_with("bfi")) %>% 
+    group_by(PerUn) %>% 
+    summarise(across(bfi1:bfi26, 
+                     mean, na.rm = TRUE)
+              ) %>% 
+    ungroup() %>% 
+    rename_at(vars(bfi1:bfi26), ~ paste0("itrait", 1:26)
+              )
+# Merge
+df <- list(perceiver_target_data,
+           perceiver_target_affect_EA,
+           ind_diffs_self,
+           informant_bfi,
+           aggregated_informant_data) %>% 
+  reduce(left_join)
+
+rm(list = gdata::keep(df))
 ```
@@
 # affect
+samEACaggdata <- rio::import(here::here("data", "samdata.csv"))
 
@@
 
-summary(SAM1)
-(SAM1)
+sjPlot::tab_model(SAM1)
+
+## save random effects
+lapply(ranef(SAM1), write.table, 
+       append = TRUE, 
+       file = here::here("data", "raneff from SAM1 for TRT.csv"))
+
+## extract empirical bayesian estimates for targets
+EBTRTtar <- ranef(SAM1)$TarUn
+colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
+EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
+map_dbl(EBTRTtar, sd)
+
+## extract empirical bayesian estimates for perceivers
+EBTRTper <- ranef(SAM1)$PerUn
+EBTRTper$PerUn<-as.numeric(row.names(EBTRTper))
+map_dbl(EBTRTper,sd)
+
+## Density plots for random effects will be here
 

### 2022-05-16 manuscript.Rmd
update the html

@@
 library(lmerTest)
+library(rio)
 ```
@@
 # import data for exploratory predictors
-paths <- dir_ls(here("data"))
+paths <- fs::dir_ls(here::here("data"))
 df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)
@@
 walk2(df_names, paths, ~{
-  assign(.x, import(.y), envir = .GlobalEnv)
+  assign(.x, import(.y), 
+         envir = .GlobalEnv)
 })
@@
 # rename
+library(magrittr)
 ind_diffs_self %<>% 
@@
 ## Descriptive statistics for Empathic Accuracy
-```{r}
+```{r, include = FALSE}
 descriptive_df <-
@@
 ```
+
 Table 1 represents descriptive statistics for all the variables in the present study.
@@
 # affect
-samEACaggdata <- rio::import(here::here("data", "samdata.csv"))
+samEACaggdata <- import(here::here("data", "c_affect.csv"))
+
+samEAC_null <- lmer (Part ~ 1 + 
+                  (1|PerUn) + 
+                  (1|TarUn) + 
+                  (1|DyUn), 
+                data = samEACaggdata)
+
+sjPlot::tab_model(samEAC_null)
 
@@
 EBTRTtar <- ranef(SAM1)$TarUn
-colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
 EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
@@
 ## fit a model for each perceiver
-models_dyad <- 
-samdata %>% 
-  group_by(PerUn) %>% 
-  nest() %>% 
-  mutate(models = map(data, ~ {
-
-    lm(ptrait ~ targSRrC + AvgtraitC, 
-              data = .x)
-
-  }
-                      )
-         )
+# models_dyad <- 
+# samdata %>% 
+#   group_by(PerUn) %>% 
+#   nest() %>% 
+#   mutate(models = map(data, ~ {
+#     
+#     lm(ptrait ~ targSRrC + AvgtraitC, 
+#               data = .x)
+#     
+#   }
+#                       )
+#          )
 ```
@@
 # affect
+samEAC <- lmer (Part ~ targSRrC + NormC + 
+                  (targSRrC + NormC|PerUn) + 
+                  (targSRrC + NormC|TarUn) + 
+                  (targSRrC + NormC|DyUn), 
+                data = samEACaggdata)
+
+summary(samEAC)
 

### 2022-05-16 manuscript.Rmd
update html again

@@
 # Results {.tabset .tabset-fade}
+
+**THIS IS A VERY ROUGH DRAFT :) **
+
 ```{r, include = FALSE}
@@
 
-## Descriptive statistics for Empathic Accuracy
+## Descriptive statistics
 ```{r, include = FALSE}
@@
 
-## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits
+## Variance decomposition
 
@@
 # personality
-samdata <- rio::import(here::here("data", "samdata.csv"))
+samdata <- import(here::here("data", "samdata.csv"))
 
@@
 sjPlot::tab_model(samEAC_null)
-
 ```
@@
 # thought
+eaSRMdata <- import(here::here("data", "d_thought.csv"))
 
+# overall EA
+SRMdat1 <- lmer(EA100 ~ 
+                   (1|PerUn) + 
+                   (1|TarUn) + 
+                   (1|DyUn) + 
+                   (1|Group), 
+                 data = eaSRMdata)
+
+sjPlot::tab_model(SRMdat1)
 ```
 
-## Interpersonal accuracy for thoughts, affect, and personality traits
+## Interpersonal accuracy
 
@@
 
-## Density plots for random effects will be here
+## Density plots for random effects will be placed here
 
 ## fit a model for each perceiver
-# models_dyad <- 
-# samdata %>% 
-#   group_by(PerUn) %>% 
-#   nest() %>% 
-#   mutate(models = map(data, ~ {
-#     
-#     lm(ptrait ~ targSRrC + AvgtraitC, 
-#               data = .x)
-#     
-#   }
-#                       )
-#          )
+models_dyad <-
+samdata %>%
+  group_by(PerUn) %>%
+  nest() %>%
+  mutate(models = map(data, ~ {
+
+    lm(ptrait ~ targSRrC + AvgtraitC,
+              data = .x)
+
+  }
+                      )
+         )
 ```
@@
 
-summary(samEAC)
+sjPlot::tab_model(samEAC)
 
@@
 # thought
+# baseline accuracy
+normEASRM<- lmer(BaselineEA100 ~ 
+                   (1|PerUn) + 
+                   (1|TarUn) + 
+                   (1|DyUn) + 
+                   (1|Group), 
+                 data = eaSRMdata)
 
+# corrected for baseline
+diffEASRM<- lmer(CrrctdEAnoneg ~ 
+                    (1|PerUn) + 
+                    (1|TarUn) + 
+                    (1|DyUn) + 
+                    (1|Group), 
+                  data = eaSRMdata)
+
+sjPlot::tab_model(normEASRM, diffEASRM)
 ```
@@
 ## Predictors of interpersonal accuracy
+
+WILL WORK ON THIS LATER.
 

### 2022-05-19 manuscript.Rmd
select variables and fix the title

@@
 ---
-title: "Target Readability in Interpersonal Accuracy"
+title: "Interpersonal Accuracy of Thoughts, Affect, and Personality Traits"
 author: "Murat Kezer"
@@
 rm(list = gdata::keep(df))
+
+# select relevant variables
+df <- df %>% 
+  select(
+    PerUn:Group, # id variables
+    EA100, # emphatic accuracy (EA) for thoughts out of 100
+    sex:race_text, # demographic variables
+    strait1:strait26, # perceivers' self-reported personality traits
+    imp1:imp16, # rapport during the interaction
+    ptrait1:ptrait26, # perception of targets' personality traits
+    targSR1:targSR26, # targets' self-reported personality traits
+    Self1:Self120, # perceivers' self-reported continuous affect
+    Part1:Part120, # perception of targets'continuous affect
+    TargSR1:TargSR120, # targets' self-reported continuous affect
+    as1:as13, # attachment styles
+    auth1:auth12rc, # authenticity
+    mask1:mask13, # masking
+    ntb1:ntb10, # need to belong
+    ucla1:ucla20rc, # ucla loneliness scale
+    fne1:fne12, # fear of negative evaluation
+    beq1:beq16, # berkeley expressivity questionnaire
+    erq1:erq10, # emotion regulation (expressive suppression)
+    rse1:rse10rc, # rosenberg self-esteem
+    sat1:sat5, # satistaction with life
+    pow1:pow8, # sense of power
+    sias1:sias12, # social interaction anxiety scale
+    InsecAtt:SIAPSc, # composite variables
+    InformantTot, # number of informants for targets
+    strait4rc:strait25rc, # perceivers' traits reversed and centered
+    Extr:Trust, # composite variables for personality traits
+    itrait1:itrait26, # informant reports of targets' personality traits
+    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
+  ) %>% 
+  arrange(PerUn, TarUn, DyUn, Group)
+
+# rename variables for a final time
+
 ```

### 2022-05-20 manuscript.Rmd
peer review comments

@@
 # import functions
-source("functions.R")
+source("functions.R") #this is a cool way to use another script, thanks!
 
@@
 )
+
+#this table can have the same formatting as others.
 ```
@@
 
-sjPlot::tab_model(null1)
+sjPlot::tab_model(null1) #nice package fot tables
 ```
@@
 "This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."
+
+<!-- Peer review -->
+
+<!-- I really liked the look and feel of your manuscript!
+`.tabset-fade` had a nice look.
+Also thanks for introducing the `source()` function and `the sjPlot::tab_model()` - I can see myself using these.
+Sometimes when reporting statistic and equaltions in the markdown, I prefer using the latex format.
+Basically by enclosing in single dollar sign or double dollar sign (puts it in a new line) So, $M_{age}$, or $$M_{age}$$.
+Good luck with the manuscript.
+-->

### 2022-05-21 manuscript.Rmd
Comments

--- 2022-05-19 manuscript.Rmd
@@
 library(tidyverse)
-library(lme4)
+library(lme4) #Don't know why, but this wasn't immediately working
 library(lmerTest)
@@
 
-sjPlot::tab_model(SRMdat1)
+sjPlot::tab_model(SRMdat1) #this is really cool
 ```

### 2022-05-23 manuscript.Rmd

--- 2022-05-19 manuscript.Rmd
@@
 
+> This project is really fabulously done - the output is very clear and readable.
+If you're planning on continuing the manuscript in r, have you thought about using [Pandoc](https://pandoc.org/MANUAL.html#citations) as your citation manager?
+I don't know if it's worth the learning curve from what I know about your relationship to these data, but it may be something to check out if you want :-)
+
 # Results {.tabset .tabset-fade}
@@
 **THIS IS A VERY ROUGH DRAFT :) **
+
+> Sourcing your functions from a separate R script is a really good idea - it helps clean your code AND makes the functions easier to find (a problem I have when I have more than 2 in a script)
 
@@
 # rename
-library(magrittr)
+require(magrittr) # If this is a late addition, I assume you'll put it up with your other libraries , but if you need specifically magrittr for the following scripts, I wonder if require() will make this more reproducible?
 ind_diffs_self %<>% 
@@
   var = names(descriptive_df),
-  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
-  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
-)
+  mean = map_dbl(descriptive_df, mean, na.rm = TRUE) %>% round(., 2),
+  sd = map_dbl(descriptive_df, sd, na.rm = TRUE) %>% round(., 2),
+) %>% knitr::kable()
 ```
@@
 Table 1 represents descriptive statistics for all the variables in the present study.
+
+> I know you already know about Kable, but I added it (and rounded the data) above because it was a simple addition - feel free to keep or not (obviously).
 
@@
 
+> These analyses are really solid anaylitic work and I'm very excited to see where they go from here!
+You'll know better than I what you want to do with these, but can the emmeans package be useful for lmer objects?
+I've only used it with glm objects but *love* its simplicity :)
+
 ```{r}
@@
               data = .x)
-
   }

### 2022-05-23 manuscript.Rmd
Peer review from Manuel Vazquez

--- 2022-05-21 manuscript.Rmd
@@
 library(tidyverse)
-library(lme4) #Don't know why, but this wasn't immediately working
+library(lme4)
 library(lmerTest)
@@
 ```{r}
+# Peer Review: Perhaps you can use a package like the "gt" package to format the table 
 table1
@@
 
-sjPlot::tab_model(SRMdat1) #this is really cool
+sjPlot::tab_model(SRMdat1)
 ```
@@
 sjPlot::tab_model(normEASRM, diffEASRM)
+
+#PEER REVIEW: I notice you are writing very similar models across different outcomes, is there an option to create a function and reduce some of the repetitive code?
 ```
@@
 "This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."
+
+#PEER REVIEW: Random note, I used to work with Dr. Karyn Lewis when she was at Education Northwes :)

### 2022-05-23 manuscript.Rmd
peer review futing

--- 2022-05-21 manuscript.Rmd
@@
 # import functions
-source("functions.R")
+source("functions.R") # good idea to source functions here~
 
@@
 
-sjPlot::tab_model(null1)
+sjPlot::tab_model(null1) # Good to see that you are using this package. Tables look neat!
 ```

### 2022-05-24 manuscript.Rmd
Peer Review Ksenia

@@
 
+##data cleaning is very concise and efficient!!
+
 ```{r, include = FALSE}
 # import functions
-source("functions.R") # good idea to source functions here~
+source("functions.R") ## semms very useful! Made a note for myself
 
@@
 
-sjPlot::tab_model(null1) # Good to see that you are using this package. Tables look neat!
+sjPlot::tab_model(null1)
 ```
@@
 
+#probably a good idea to create a function that you can reuse, especially since random effect structure is the same
+
 sjPlot::tab_model(normEASRM, diffEASRM)

### 2022-05-24 manuscript.Rmd
EK Peer Review
Peer Review for EDLD 653

--- 2022-05-23 manuscript.Rmd
@@
 # import functions
-source("functions.R") # good idea to source functions here~
+source("functions.R")
 
@@
 "This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."
+
+###EK Peer Review
+
+#Strengths
+1. Reproducibility is great! Having some knitting issues with the model dyad portion, but overall the functions file and structure of the tidying and analysis are easy to follow.
+2. Using functional programming all over the place! The walk2 at the beginning of the results section is particularly nice.
+3. I don't fully understand the data or analyses that were run here, however the thorough comments were enough to get me the gist, as well as understand the functions I was not familiar with yet.
+
+One thing I learned: use of the rm function to clean the environment, that might be helpful if you were having memory issues with the r environment.
+
+One area that could be improved: very small, could write a wrapper function for lmer that allows you to pass the data, left side formula value, and numerator to use on the right side.

### 2022-05-24 manuscript.Rmd
ids

--- 2022-05-23 manuscript.Rmd
@@
 
-**THIS IS A VERY ROUGH DRAFT :) **
-
 ```{r, include = FALSE}
 # import functions
-source("functions.R") # good idea to source functions here~
+source("functions.R")
 
@@
 # rename variables for a final time
+ids <- paste0(c("perceiver", "target", "dyad", "group"), "id")
 

### 2022-05-24 manuscript.Rmd
rename vars

@@
 library(rio)
+library(magrittr)
 ```
@@
 # rename
-library(magrittr)
 ind_diffs_self %<>% 
@@
     sex:race_text, # demographic variables
+    imp1:imp16, # rapport during the interaction
     strait1:strait26, # perceivers' self-reported personality traits
-    imp1:imp16, # rapport during the interaction
     ptrait1:ptrait26, # perception of targets' personality traits
@@
     InformantTot, # number of informants for targets
-    strait4rc:strait25rc, # perceivers' traits reversed and centered
     Extr:Trust, # composite variables for personality traits
@@
 # rename variables for a final time
-ids <- paste0(c("perceiver", "target", "dyad", "group"), "id")
+ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
+rapport <- paste0("rapport", 1:16)
+personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
+                   ~ paste0(.x, 1:26)) |> unlist()
+affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
+              ~ paste0(.x, 1:120)) |> unlist()
+sbw <- paste0("swb", 1:5)
+informant <- paste0("informant_trait", 1:26)
+
+df <- df %>% 
+  rename_at(vars(c(PerUn:Group, imp1:imp16, strait1:TargSR120, sat1:sat5,
+                 itrait1:itrait26)),  ~
+            c(ids, rapport, personality, affect, sbw, informant))
 

### 2022-05-25 functions.R
function to get reliability metrics
alpha and omega

@@ -1,3 +1,20 @@
+# Reliability
+get_reliability <- function(df = df, vars, var_names){
+  
+  alphas <- psych::alpha(df[vars])$total$raw_alpha %>% round(., 2)
+  omegas <- psych::omega(df[vars])$omega.tot %>% 
+    round(., 2) %>% 
+    suppressWarnings()
+  
+  data.frame(
+    
+    vars = var_names,
+    alpha = alphas,
+    omega = omegas
+  )
+  
+}
+
 # STANDARD ERROR
 std <- function(x) sd(x)/sqrt(length(x))
 

### 2022-05-25 items_reliability.R
items and vars for reliability and descriptives

@@ -1,0 +1,68 @@
+# items
+insecure_att <- c("as1rc", "as2", "as3rc", "as4rc", "as5")
+avoid_att <- c("as6", "as7", "as8", "as9")
+anx_att <- c("as10", "as11", "as12rc", "as13")
+
+authenticity <- c("auth1", "auth2rc", "auth3rc", "auth4rc", 
+                  "auth5rc", "auth6rc", "auth7rc", "auth8", 
+                  "auth9", "auth10rc", "auth11", "auth12rc")
+
+masking <- c("mask1", "mask2", "mask3", "mask4", "mask5", 
+             "mask6", "mask7", "mask8", "mask9", "mask10rc", 
+             "mask11", "mask12", "mask13")
+
+ntb <- c("ntb1rc", "ntb2", "ntb3rc", "ntb4", "ntb5", 
+         "ntb6", "ntb7rc", "ntb8", "ntb9", "ntb10")
+
+loneliness <- c("ucla1rc", "ucla2", "ucla3", "ucla4", "ucla5rc", 
+                "ucla6rc", "ucla7", "ucla8", "ucla9rc", "ucla10rc", 
+                "ucla11", "ucla12", "ucla13", "ucla14", "ucla15rc", 
+                "ucla16rc", "ucla17", "ucla18", "ucla19rc", "ucla20rc")
+
+fne <- paste0("fne", 1:12)
+
+pos_express <- c('beq1', 'beq4', 'beq6', 'beq10')
+neg_express <- c('beq3rc', 'beq5', 'beq8rc', 'beq9rc', 'beq13', 'beq16')
+impulse_str <- c('beq2', 'beq7', 'beq11', 'beq12', 'beq14', 'beq15')
+
+suppression <- c('erq2', 'erq4', 'erq6', 'erq9')
+reappraisal <- c('erq1', 'erq3', 'erq5', 'erq7', 'erq8', 'erq10')
+
+s_esteem <- c('rse1', 'rse2', 'rse3rc', 'rse4', 'rse5rc', 
+              'rse6', 'rse7', 'rse8rc', 'rse9rc', 'rse10rc')
+
+swb <- paste0('swb', 1:5)
+
+sense_of_power <- c('pow1', 'pow2rc', 'pow3', 'pow4rc', 
+                    'pow5', 'pow6rc', 'pow7rc', 'pow8')
+
+si_anx <- paste0('sias', 1:6)
+s_phobia <- paste0('sias', 7:12)
+
+## lists
[…]

### 2022-05-25 items_reliability.R
add personality items

@@ -39,11 +39,57 @@ sense_of_power <- c('pow1', 'pow2rc', 'pow3', 'pow4rc',
 si_anx <- paste0('sias', 1:6)
 s_phobia <- paste0('sias', 7:12)
 
+per_open <- c('perceiver_trait13', 'perceiver_trait22')
+per_cons <- c('perceiver_trait6', 'perceiver_trait15rc',
+              'perceiver_trait19', 'perceiver_trait26')
+per_extra <- c('perceiver_trait1', 'perceiver_trait3', 'perceiver_trait7',
+               'perceiver_trait8rc', 'perceiver_trait9', 
+               'perceiver_trait21rc', 'perceiver_trait25rc')
+per_agre <- c('perceiver_trait10rc', 'perceiver_trait14',
+              'perceiver_trait18rc', 'perceiver_trait23')
+per_neur <- c('perceiver_trait4rc', 'perceiver_trait12', 
+              'perceiver_trait16rc', 'perceiver_trait20')
+per_intel <- c('perceiver_trait2', 'perceiver_trait17', 'perceiver_trait24')
+per_trust <- c('perceiver_trait5', 'perceiver_trait11')
+
+tar_open <- c('target_trait13', 'target_trait22')
+tar_cons <- c('target_trait6', 'target_trait15rc',
+              'target_trait19', 'target_trait26')
+tar_extra <- c('target_trait1', 'target_trait3', 'target_trait7',
+               'target_trait8rc', 'target_trait9', 
+               'target_trait21rc', 'target_trait25rc')
+tar_agre <- c('target_trait10rc', 'target_trait14',
+              'target_trait18rc', 'target_trait23')
+tar_neur <- c('target_trait4rc', 'target_trait12', 
+              'target_trait16rc', 'target_trait20')
+tar_intel <- c('target_trait2', 'target_trait17', 'target_trait24')
+tar_trust <- c('target_trait5', 'target_trait11')
+
+judg_open <- c('judgment_trait13', 'judgment_trait22')
+judg_cons <- c('judgment_trait6', 'judgment_trait15rc',
+              'judgment_trait19', 'judgment_trait26')
+judg_extra <- c('judgment_trait1', 'judgment_trait3', 'judgment_trait7',
+               'judgment_trait8rc', 'judgment_trait9', 
+               'judgment_trait21rc', 'judgment_trait25rc')
+judg_agre <- c('judgment_trait10rc', 'judgment_trait14',
[…]

### 2022-05-29 manuscript.Rmd
recode 99 into NA

@@
 personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
-                   ~ paste0(.x, 1:26)) |> unlist()
+                   ~ paste0(.x, 1:26)) %>% unlist()
 affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
-              ~ paste0(.x, 1:120)) |> unlist()
+              ~ paste0(.x, 1:120)) %>% unlist()
 sbw <- paste0("swb", 1:5)
@@
 
+# recode 99s into NA
+recode_99s <- 
+psych::describe(df[-9]) %>% 
+  rownames_to_column() %>% 
+  filter(max == 99) %>% 
+  select(rowname)
+
+df2 <-  
+df %>% 
+  mutate(
+    across(recode_99s$rowname, ~ na_if(.x, 99))
+  )
 ```
@@
 ```{r, include = FALSE}
+# descriptives
 descriptive_df <-
@@
 ```{r}
-# Peer Review: Perhaps you can use a package like the "gt" package to format the table 
 table1
@@
 sjPlot::tab_model(normEASRM, diffEASRM)
-
-#PEER REVIEW: I notice you are writing very similar models across different outcomes, is there an option to create a function and reduce some of the repetitive code?
 ```
@@
 "This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."
-
-#PEER REVIEW: Random note, I used to work with Dr. Karyn Lewis when she was at Education Northwes :)

### 2022-05-29 manuscript.Rmd
reverse coding

@@
 
-df2 <-  
+df <-  
 df %>% 
@@
   )
+
+# reverse coding
+negative_keyed_items <- c('perceiver_trait15', 'perceiver_trait8',
+                          'perceiver_trait21', 'perceiver_trait25',
+                          'perceiver_trait10', 'perceiver_trait18',
+                          'perceiver_trait4', 'perceiver_trait16',
+                          'target_trait15', 'target_trait8',
+                          'target_trait21', 'target_trait25',
+                          'target_trait10', 'target_trait18',
+                          'target_trait4', 'target_trait16',
+                          'judgment_trait15', 'judgment_trait8',
+                          'judgment_trait21', 'judgment_trait25',
+                          'judgment_trait10', 'judgment_trait18',
+                          'judgment_trait4', 'judgment_trait16')
+
+df <- 
+df %>% 
+  mutate(
+    across(all_of(negative_keyed_items), subtract_8)
+  )
+
 ```

### 2022-05-29 functions.R

@@ -15,6 +15,9 @@ get_reliability <- function(df = df, vars, var_names){
   
 }
 
+# Subtract 8 for reverse coding
+subtract_8 <- function(x) {8 - x}
+
 # STANDARD ERROR
 std <- function(x) sd(x)/sqrt(length(x))
 

### 2022-05-29 manuscript.Rmd
internal consistency

@@
   )
-
 ```
@@
 )
+
+# internal consistency
+source("items_reliability.R")
+
+df_desc <- df %>% 
+  distinct(perceiver_id)
+
+map2_dfr(item_list, variable_names, ~ 
+           get_reliability(df = df_desc, 
+                           vars = .x, 
+                           var_names = .y)
+         )
+
+df %>% 
+  select(rse1:rse10rc) %>% 
+  names()
 ```

### 2022-05-30 manuscript.Rmd
fix reverse coding and internal consistency

@@
 ```{r, include = FALSE}
-# import functions
-source("functions.R")
-
 # import data for exploratory predictors
@@
 rm(list = gdata::keep(df))
+
+# import functions
+source("functions.R")
 
@@
 
-df <- 
+df_reverse <- 
   df %>% 
-  mutate(
-    across(all_of(negative_keyed_items), subtract_8)
-  )
+  select(perceiver_id:group_id,
+         negative_keyed_items)
+
+df_reverse <- 
+df_reverse %>% 
+  mutate(across(all_of(negative_keyed_items), subtract_8)) %>% 
+  rename_at(vars(negative_keyed_items), ~ paste0(negative_keyed_items, "rc"))
+
+df <- left_join(df, df_reverse)
 ```
@@
 df_desc <- df %>% 
-  distinct(perceiver_id)
+  distinct(perceiver_id, 
+           .keep_all = TRUE)
 
@@
            get_reliability(df = df_desc, 
-                           vars = .x, 
+                           items = .x, 
                            var_names = .y)
          )
+```
 
-df %>% 
-  select(rse1:rse10rc) %>% 
-  names()
-```
+per_open, per_cons, per_extra, per_agre, per_neur,
+per_intel, per_trust,
+tar_open, tar_cons, tar_extra, tar_agre, tar_neur,
+tar_intel, tar_trust,
+judg_open, judg_cons, judg_extra, judg_agre, judg_neur,
+judg_intel, judg_trust
 

### 2022-05-30 functions.R

@@ -1,8 +1,11 @@
 # Reliability
-get_reliability <- function(df = df, vars, var_names){
+get_reliability <- function(df, items, var_names){
   
-  alphas <- psych::alpha(df[vars])$total$raw_alpha %>% round(., 2)
-  omegas <- psych::omega(df[vars])$omega.tot %>% 
+  alphas <- psych::alpha(df[items], check.keys = TRUE)$total$raw_alpha %>% 
+    round(., 2) %>% 
+    suppressWarnings()
+  
+  omegas <- psych::omega(df[items], plot = FALSE)$omega.tot %>% 
     round(., 2) %>% 
     suppressWarnings()
   

### 2022-05-30 items_reliability.R

@@ -130,6 +130,3 @@ variable_names <- list("Insecure Attachment",
                        'Judgment Neuroticism',
                        'Judgment Intelligence',
                        'Judgment Trustworthiness')
-
-
-

### 2022-05-30 manuscript.Rmd
Table 1

@@
     InformantTot, # number of informants for targets
-    Extr:Trust, # composite variables for personality traits
+    Extr:Trust, # composite variables for personality traits of perceivers
     itrait1:itrait26, # informant reports of targets' personality traits
@@
 # descriptives
-descriptive_df <-
+vars_desc <-
 df %>% 
@@
     FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
-    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
-  )
-
-table1 <-
-tibble(
-  var = names(descriptive_df),
-  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
-  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
-)
-
-# internal consistency
-source("items_reliability.R")
+    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust
+  ) %>% 
+  names()
 
@@
 
+tab_desc <-  get_descriptives(df_desc[vars_desc])
+
+# internal consistency
+source("items_reliability.R")
+
+int_cons <- 
 map2_dfr(item_list, variable_names, ~ 
@@
          )
+
+# table 1
+table1 <- bind_cols(tab_desc, int_cons) %>% 
+  select(Variables = vars, N_Valid:Max, Alpha:Omega)
 ```
-
-per_open, per_cons, per_extra, per_agre, per_neur,
-per_intel, per_trust,
-tar_open, tar_cons, tar_extra, tar_agre, tar_neur,
-tar_intel, tar_trust,
-judg_open, judg_cons, judg_extra, judg_agre, judg_neur,
-judg_intel, judg_trust
 
@@
 ```{r}
-table1
+kable_style(table1, 
+            title = "<center><b>Table 1: Descriptive Statistics and Internal Consistency</center></b>")
 ```

### 2022-05-30 functions.R

@@ -5,15 +5,16 @@ get_reliability <- function(df, items, var_names){
     round(., 2) %>% 
     suppressWarnings()
   
-  omegas <- psych::omega(df[items], plot = FALSE)$omega.tot %>% 
+  omegas <- psych::omega(df[items], plot = FALSE, nfactors = 1)$omega.tot %>% 
     round(., 2) %>% 
-    suppressWarnings()
+    suppressWarnings() %>% 
+    suppressMessages()
   
   data.frame(
     
     vars = var_names,
-    alpha = alphas,
-    omega = omegas
+    Alpha = alphas,
+    Omega = omegas
   )
   
 }
@@ -25,13 +26,23 @@ subtract_8 <- function(x) {8 - x}
 std <- function(x) sd(x)/sqrt(length(x))
 
 # SUMMARY FUNCTION
-get_descrip <- function(dat, var1){
-  dat %>% summarize(n = n(),
-                    mean = mean(var1, na.rm = TRUE), 
-                    sd = sd(var1, na.rm = TRUE),
-                    median = median(var1, na.rm = TRUE),
-                    min = min(var1, na.rm = TRUE),
-                    max = max(var1, na.rm = TRUE))
+get_desc <- list(
+  
+  N_Valid = function(var) {sum(complete.cases(var))},
+  Mean = function(var) {round(mean(var, na.rm = TRUE), 2)},
+  SD = function(var) {round(sd(var, na.rm = TRUE), 2)},
+  Min = function(var) {round(min(var, na.rm = TRUE), 2)},
+  Max = function(var) {round(max(var, na.rm = TRUE), 2)}
+  
+)
+
+get_desc2 <- 
+  function(column) {
+    map_df(get_desc, ~.x(column))
+  }
+
+get_descriptives <- function(df) {
+  map_df(df, get_desc2, .id = "column")
 }
 
 # SUMMARY FUNCTION by GROUP
@@ -48,14 +59,14 @@ group_means <- function(data, outcome, ...) {
 }  
 
 # KABLE STYLING
-kable_style <- function(data){
+kable_style <- function(data, title){
   
   data <- as_tibble(data)
   
-  kable(data, digits = 2, align = "c") %>% 
-    kable_styling(bootstrap_options = c("striped"),
-                  full_width = FALSE) %>% 
-    row_spec(0, background = "gray", color = "white")  
+  knitr::kable(data, digits = 2, align = "c", caption = title) %>% 
[…]

### 2022-05-30 items_reliability.R

@@ -52,44 +52,13 @@ per_neur <- c('perceiver_trait4rc', 'perceiver_trait12',
 per_intel <- c('perceiver_trait2', 'perceiver_trait17', 'perceiver_trait24')
 per_trust <- c('perceiver_trait5', 'perceiver_trait11')
 
-tar_open <- c('target_trait13', 'target_trait22')
-tar_cons <- c('target_trait6', 'target_trait15rc',
-              'target_trait19', 'target_trait26')
-tar_extra <- c('target_trait1', 'target_trait3', 'target_trait7',
-               'target_trait8rc', 'target_trait9', 
-               'target_trait21rc', 'target_trait25rc')
-tar_agre <- c('target_trait10rc', 'target_trait14',
-              'target_trait18rc', 'target_trait23')
-tar_neur <- c('target_trait4rc', 'target_trait12', 
-              'target_trait16rc', 'target_trait20')
-tar_intel <- c('target_trait2', 'target_trait17', 'target_trait24')
-tar_trust <- c('target_trait5', 'target_trait11')
-
-judg_open <- c('judgment_trait13', 'judgment_trait22')
-judg_cons <- c('judgment_trait6', 'judgment_trait15rc',
-              'judgment_trait19', 'judgment_trait26')
-judg_extra <- c('judgment_trait1', 'judgment_trait3', 'judgment_trait7',
-               'judgment_trait8rc', 'judgment_trait9', 
-               'judgment_trait21rc', 'judgment_trait25rc')
-judg_agre <- c('judgment_trait10rc', 'judgment_trait14',
-              'judgment_trait18rc', 'judgment_trait23')
-judg_neur <- c('judgment_trait4rc', 'judgment_trait12', 
-              'judgment_trait16rc', 'judgment_trait20')
-judg_intel <- c('judgment_trait2', 'judgment_trait17', 'judgment_trait24')
-judg_trust <- c('judgment_trait5', 'judgment_trait11')
-
-
 ## lists
 item_list <- list(insecure_att, avoid_att, anx_att, authenticity,
                   masking, ntb, loneliness, fne, pos_express,
                   neg_express, impulse_str, suppression, reappraisal,
                   s_esteem, swb, sense_of_power, si_anx, s_phobia,
                   per_open, per_cons, per_extra, per_agre, per_neur,
-                  per_intel, per_trust,
-                  tar_open, tar_cons, tar_extra, tar_agre, tar_neur,
-                  tar_intel, tar_trust,
[…]

### 2022-06-02 manuscript.Rmd
update code for reverse coding

@@
 rapport <- paste0("rapport", 1:16)
-personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
+personality <- map(c("perceiver_trait", "judgment_trait", "target_trait"),
                    ~ paste0(.x, 1:26)) %>% unlist()
@@
 
-df_reverse <- 
+df <- 
   df %>% 
-  select(perceiver_id:group_id,
-         negative_keyed_items)
+  mutate_at(list(rc = ~subtract_8(.)),
+            .vars = vars(negative_keyed_items)
+            )
 
-df_reverse <- 
-df_reverse %>% 
-  mutate(across(all_of(negative_keyed_items), subtract_8)) %>% 
-  rename_at(vars(negative_keyed_items), ~ paste0(negative_keyed_items, "rc"))
-
-df <- left_join(df, df_reverse)
 ```
@@
 
-Table 1 represents descriptive statistics for all the variables in the present study.
+Table 1 represents descriptive statistics as well as internal consistency metrics (i.e., alpha and omega) for predictors of interpersonal accuracy.
 
@@
 
+```{r, include = FALSE}
+# Create, clean and format data for analyses
+## Personality
+
+```
+
 ```{r}
 # personality
-samdata <- import(here::here("data", "samdata.csv"))
+df_personality <- import(here::here("data", "samdata.csv"))
 
-samdata <-
-  samdata %>% 
+df_personality <-
+  df_personality %>% 
   mutate(
@@
 null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
-               data = samdata)
+               data = df_personality)
 
@@
                   (1|TarUn) + 
-                  (1|DyUn), 
+                  (1|DyUn) +
+                    (1|Group), 
                 data = samEACaggdata)
@@
 sjPlot::tab_model(samEAC_null)
+
+summary(samEAC_null)
 ```

### 2022-06-02 functions.R

@@ -22,9 +22,6 @@ get_reliability <- function(df, items, var_names){
 # Subtract 8 for reverse coding
 subtract_8 <- function(x) {8 - x}
 
-# STANDARD ERROR
-std <- function(x) sd(x)/sqrt(length(x))
-
 # SUMMARY FUNCTION
 get_desc <- list(
   
@@ -45,19 +42,6 @@ get_descriptives <- function(df) {
   map_df(df, get_desc2, .id = "column")
 }
 
-# SUMMARY FUNCTION by GROUP
-group_means <- function(data, outcome, ...) {
-  out <- enquo(outcome)
-  
-  data %>%
-    group_by(...) %>%
-    summarize(Mean = mean(!!out, na.rm = TRUE),
-              SD = sd(!!out, na.rm = TRUE),
-              Min = min(!!out, na.rm = TRUE),
-              Max = max(!!out, na.rm = TRUE)
-    )
-}  
-
 # KABLE STYLING
 kable_style <- function(data, title){
   
@@ -65,16 +49,8 @@ kable_style <- function(data, title){
   
   knitr::kable(data, digits = 2, align = "c", caption = title) %>% 
     kableExtra::kable_styling(bootstrap_options = c("striped"),
-                              full_width = FALSE) %>% 
+                              full_width = FALSE, 
+                              fixed_thead = TRUE) %>% 
     kableExtra::row_spec(0, background = "gray", color = "white")  
   
-}
-
-# BARPLOT THEME
-bp_theme <- function(...) {
-  theme_minimal(...) +
-    theme(panel.grid.major.y = element_blank(),
-          panel.grid.minor.x = element_blank(),
-          panel.grid.major.x = element_line(color = "gray80"),
-          plot.title.position = "plot")
 }

### 2022-06-02 items_reliability.R

@@ -40,15 +40,15 @@ si_anx <- paste0('sias', 1:6)
 s_phobia <- paste0('sias', 7:12)
 
 per_open <- c('perceiver_trait13', 'perceiver_trait22')
-per_cons <- c('perceiver_trait6', 'perceiver_trait15rc',
+per_cons <- c('perceiver_trait6', 'perceiver_trait15_rc',
               'perceiver_trait19', 'perceiver_trait26')
 per_extra <- c('perceiver_trait1', 'perceiver_trait3', 'perceiver_trait7',
-               'perceiver_trait8rc', 'perceiver_trait9', 
-               'perceiver_trait21rc', 'perceiver_trait25rc')
-per_agre <- c('perceiver_trait10rc', 'perceiver_trait14',
-              'perceiver_trait18rc', 'perceiver_trait23')
-per_neur <- c('perceiver_trait4rc', 'perceiver_trait12', 
-              'perceiver_trait16rc', 'perceiver_trait20')
+               'perceiver_trait8_rc', 'perceiver_trait9', 
+               'perceiver_trait21_rc', 'perceiver_trait25_rc')
+per_agre <- c('perceiver_trait10_rc', 'perceiver_trait14',
+              'perceiver_trait18_rc', 'perceiver_trait23')
+per_neur <- c('perceiver_trait4_rc', 'perceiver_trait12', 
+              'perceiver_trait16_rc', 'perceiver_trait20')
 per_intel <- c('perceiver_trait2', 'perceiver_trait17', 'perceiver_trait24')
 per_trust <- c('perceiver_trait5', 'perceiver_trait11')
 

### 2022-06-02 manuscript.Rmd
rapport + clean trait data

@@
                           'judgment_trait10', 'judgment_trait18',
-                          'judgment_trait4', 'judgment_trait16')
+                          'judgment_trait4', 'judgment_trait16',
+                          'rapport12', 'rapport13', 'rapport14',
+                          'rapport15')
 
@@
 
+# composite var for rapport
+df <- 
+  df %>% 
+  mutate(rapport = rowMeans(select(., 
+                                   rapport1:rapport11,
+                                   rapport12_rc:rapport15_rc),
+                            na.rm = TRUE),
+         # other composite variables are scaled to 0-100
+         rapport = rapport - 1,
+         rapport = rapport/7 * 100,
+         rapport_c = scale(rapport, scale = FALSE)
+         ) %>% 
+  relocate(rapport, .before = informant_trait1) %>% 
+  relocate(rapport_c, .before = rapport)
 ```
@@
   select(
-    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
+    rapport, InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
     FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
@@
 # Create, clean and format data for analyses
-## Personality
+
+## Personality (self- AND informant-reports of targets)
+df_personality <-
+  df %>% 
+  select(perceiver_id:group_id,
+         judgment_trait1:target_trait26,
+         informant_trait1:informant_trait26,
+         InsecAtt:Trust, -ends_with("C"), -ASMtot, -beqtot, -SIAPS)
+
+trait_norms <- # average value for each trait
+df_personality %>% 
+  select(target_trait1:informant_trait26) %>% 
+  map_df(., mean, na.rm = TRUE) %>% 
+  pivot_longer(., cols = everything(), 
+               names_to = "item",
+               names_pattern = "(\\d+)$",
+               values_to = "norm") %>% 
+  mutate(type = c(rep("self_norm", 26), rep("inf_norm", 26))) %>% 
+  pivot_wider(names_from = "type", 
+              values_from = "norm") %>% 
+  mutate(item = as.numeric(item))
+
+df_personality <- 
+df_personality %>% 
+  pivot_longer(cols = judgment_trait1:informant_trait26,
+               names_to = c("trait", "item"),
+               names_sep = "_",
+               values_to = "rating") %>% 
+  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
+  pivot_wider(names_from = "trait",
+              values_from = "rating") %>% 
+  right_join(., trait_norms, by = "item") %>% 
+  mutate(self_dist = target - self_norm,
+         inf_dist = informant - inf_norm,
+         across(c(InsecAtt:Trust, self_norm:inf_dist), 
+                scale, scale = FALSE, center = TRUE)
+         )
 
@@
 ```{r}
-# personality
-df_personality <- import(here::here("data", "samdata.csv"))
-
-df_personality <-
-  df_personality %>% 
-  mutate(
-
-    Avgtrait = Avgtrait - 1,
-    targSRr = targSR - Avgtrait,
-
-    # Note to self: use a loop for these.
-    targSRrC = scale(targSRr, scale = FALSE, center = TRUE),
-    AvgtraitC = scale(Avgtrait, scale = FALSE, center = TRUE),
-    ptraitC = scale(ptrait, scale = FALSE, center = TRUE)
-  )
-
-## null model
-null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
+null_trait_self <- lmer(judgment ~ 
+                (1|perceiver_id) + 
+                (1|target_id) + 
+                (1|dyad_id) +
+                (1|group_id),
               data = df_personality)
-
-sjPlot::tab_model(null1)
 ```

### 2022-06-02 items_reliability.R

@@ -1,4 +1,6 @@
 # items
+rapport <- c(paste0('rapport', 1:11),
+             paste0('rapport', 12:15, '_rc'))
 insecure_att <- c("as1rc", "as2", "as3rc", "as4rc", "as5")
 avoid_att <- c("as6", "as7", "as8", "as9")
 anx_att <- c("as10", "as11", "as12rc", "as13")
@@ -53,14 +55,15 @@ per_intel <- c('perceiver_trait2', 'perceiver_trait17', 'perceiver_trait24')
 per_trust <- c('perceiver_trait5', 'perceiver_trait11')
 
 ## lists
-item_list <- list(insecure_att, avoid_att, anx_att, authenticity,
+item_list <- list(rapport, insecure_att, avoid_att, anx_att, authenticity,
                   masking, ntb, loneliness, fne, pos_express,
                   neg_express, impulse_str, suppression, reappraisal,
                   s_esteem, swb, sense_of_power, si_anx, s_phobia,
                   per_open, per_cons, per_extra, per_agre, per_neur,
                   per_intel, per_trust)
 
-variable_names <- list("Insecure Attachment", 
+variable_names <- list("Rapport",
+                       "Insecure Attachment", 
                        "Avoidant Attachment",
                        "Anxious Attachment",
                        "Authenticity",

### 2022-06-02 manuscript.Rmd
clean affect data

@@
 
-df_personality <- 
+df_personality <- # create final df for analyses
 df_personality %>% 
@@
                 scale, scale = FALSE, center = TRUE)
+         )
+## Affect
+df_affect <- 
+  df %>% 
+  select(perceiver_id:group_id,
+         target_affect1:judgment_affect120)
+
+affect_norms <- # average values
+  df_affect %>% 
+  select(target_affect1:target_affect120) %>% 
+  map_df(., mean, na.rm = TRUE) %>% 
+  pivot_longer(., cols = everything(),
+               names_to = "item",
+               names_pattern = "(\\d+)$",
+               values_to = "norm") %>% 
+  mutate(item = as.numeric(item))
+
+df_affect <- 
+  df_affect %>% 
+  pivot_longer(cols = target_affect1:judgment_affect120,
+               names_to = c("affect", "item"),
+               names_sep = "_",
+               values_to = "rating") %>% 
+  mutate(item = parse_number(item)) %>% 
+  pivot_wider(names_from = "affect",
+              values_from = "rating") %>% 
+  right_join(., affect_norms, by = "item") %>% 
+  mutate(self_dist = target - norm,
+         across(norm:self_dist, scale, scale = FALSE, center = TRUE)
          )

### 2022-06-04 manuscript.Rmd
centering and some fixes

--- 2022-06-02 manuscript.Rmd
@@
     sias1:sias12, # social interaction anxiety scale
-    InsecAtt:SIAPSc, # composite variables
-    InformantTot, # number of informants for targets
-    Extr:Trust, # composite variables for personality traits of perceivers
+    # composite variables
+    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
+    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
+    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust, 
     itrait1:itrait26, # informant reports of targets' personality traits
@@
 
+# centering
+df <- 
+  df %>% 
+  mutate_at(list(c = ~center(.)),
+            .vars = vars(InsecAtt:Trust))
+
 # composite var for rapport
@@
          ) %>% 
-  relocate(rapport, .before = informant_trait1) %>% 
-  relocate(rapport_c, .before = rapport)
+  relocate(rapport, .before = informant_trait1)
 ```
@@
          informant_trait1:informant_trait26,
-         InsecAtt:Trust, -ends_with("C"), -ASMtot, -beqtot, -SIAPS)
+         InsecAtt_c:rapport_c)
 
@@
   mutate(self_dist = target - self_norm,
-         inf_dist = informant - inf_norm,
-         across(c(InsecAtt:Trust, self_norm:inf_dist), 
-                scale, scale = FALSE, center = TRUE)
+         inf_dist = informant - inf_norm
          )
+
+## Affect
+df_affect <- 
+  df %>% 
+  select(perceiver_id:group_id,
+         target_affect1:judgment_affect120,
+         InsecAtt_c:rapport_c)
+
+affect_norms <- # average values
+  df_affect %>% 
+  select(target_affect1:target_affect120) %>% 
+  map_df(., mean, na.rm = TRUE) %>% 
+  pivot_longer(., cols = everything(),
+               names_to = "second",
+               names_pattern = "(\\d+)$",
+               values_to = "norm") %>% 
+  mutate(second = as.numeric(second))
+
+df_affect <- 
+  df_affect %>% 
+  pivot_longer(cols = target_affect1:judgment_affect120,
+               names_to = c("affect", "second"),
+               names_sep = "_",
+               values_to = "rating") %>% 
+  mutate(second = parse_number(second)) %>% 
+  pivot_wider(names_from = "affect",
+              values_from = "rating") %>% 
+  right_join(., affect_norms, by = "second") %>% 
+  mutate(self_dist = target - norm,
+         across(norm:self_dist, center)
+         )
+
+## Thought
+df_thought <- import(here::here("data", "d_thought.csv")) %>% 
+  select(PerUn, TarUn, DyUn, Group, BaselineEA:CrrctdEAnoneg) %>% 
+  rename_at(vars(PerUn:Group), ~ 
+              c("perceiver_id", "target_id", "dyad_id", "group_id")
+             ) %>% 
+  left_join(., select(df_personality, perceiver_id:group_id,
+                      InsecAtt:Trust, rapport_c))
 
@@
 
-```{r}
+```{r null models}
 null_trait_self <- lmer(judgment ~ 
@@
 
-sjPlot::tab_model(samEAC_null)
+sjPlot::tab_model(samEAC_null, null_affect)
 
 summary(samEAC_null)
+
+null_affect <- lmer(judgment ~ 1 + 
+                  (1|perceiver_id) + 
+                  (1|target_id) + 
+                  (1|dyad_id) +
+                    (1|group_id), 
+                data = df_affect)
+
 ```
@@
 # thought
-eaSRMdata <- import(here::here("data", "d_thought.csv"))
 

### 2022-06-04 functions.R

@@ -22,6 +22,9 @@ get_reliability <- function(df, items, var_names){
 # Subtract 8 for reverse coding
 subtract_8 <- function(x) {8 - x}
 
+# center
+center <- function(x) {x - mean(x, na.rm = TRUE)}
+
 # SUMMARY FUNCTION
 get_desc <- list(
   

### 2022-06-05 manuscript.Rmd
Null models - v1

@@
   mutate(self_dist = target - self_norm,
-         inf_dist = informant - inf_norm
+         inf_dist = informant - inf_norm,
+         across(self_norm:inf_dist, center)
          )
@@
              ) %>% 
-  left_join(., select(df_personality, perceiver_id:group_id,
-                      InsecAtt:Trust, rapport_c))
+  left_join(., select(df, perceiver_id:group_id,
+                      InsecAtt_c:rapport_c)) %>% 
+  rename(judgment = EA100)
 
@@
 ```{r null models}
-null_trait_self <- lmer(judgment ~ 
-                (1|perceiver_id) + 
+df_list <- list(df_personality,
+                df_affect,
+                df_thought)
+
+null_models <- df_list %>% 
+  map_dfr(
+    ~ lmer(judgment ~ (1|perceiver_id) + 
              (1|target_id) + 
-                (1|dyad_id) +
-                (1|group_id),
-              data = df_personality)
-```
+             (1|dyad_id),
+           data = .x) %>% 
+      broom.mixed::tidy()
+    )
 
-```{r}
-# affect
-samEACaggdata <- import(here::here("data", "c_affect.csv"))
+null_models %>% 
+  kable_style(title = "<center><b>Null Models</b></center>") %>% 
+  kableExtra::pack_rows("Personality", 1, 5) %>% 
+  kableExtra::pack_rows("Affect", 6, 10) %>% 
+  kableExtra::pack_rows("Thought", 11, 15)
 
-samEAC_null <- lmer (Part ~ 1 + 
-                  (1|PerUn) + 
-                  (1|TarUn) + 
-                  (1|DyUn) +
-                    (1|Group), 
-                data = samEACaggdata)
+by_model <- 
+null_models %>% 
+  mutate(model = c(rep("p", 5), rep("a", 5), rep("t", 5))
+         ) %>% 
+  group_by(model) %>% 
+  nest()
 
-sjPlot::tab_model(samEAC_null, null_affect)
+map(by_model, specr::plot_variance)
 
-summary(samEAC_null)
+fill_color <- "#377eb8"
 
-null_affect <- lmer(judgment ~ 1 + 
-                  (1|perceiver_id) + 
+null_models2 <- df_list %>% 
+  map(
+    ~ lmer(judgment ~ (1|perceiver_id) + 
              (1|target_id) + 
-                  (1|dyad_id) +
-                    (1|group_id), 
-                data = df_affect)
+             (1|dyad_id),
+           data = .x)
+    )
 
-```
+map(null_models2, performance::icc, by_group = TRUE)
 
-```{r}
-# thought
-
-# overall EA
-SRMdat1 <- lmer(EA100 ~ 
-                   (1|PerUn) + 
-                   (1|TarUn) + 
-                   (1|DyUn) + 
-                   (1|Group), 
-                 data = eaSRMdata)
-
-sjPlot::tab_model(SRMdat1)
 ```

### 2022-06-05 manuscript.Rmd
null models final

@@
 
-by_model <- 
-null_models %>% 
-  mutate(model = c(rep("p", 5), rep("a", 5), rep("t", 5))
-         ) %>% 
-  group_by(model) %>% 
-  nest()
-
-map(by_model, specr::plot_variance)
-
-fill_color <- "#377eb8"
-
 null_models2 <- df_list %>% 
@@
 
-map(null_models2, performance::icc, by_group = TRUE)
+sjPlot::tab_model(null_models2[[1]],
+                  null_models2[[2]],
+                  null_models2[[3]], 
+                  dv.labels = c("Personality", "Affect", "Thought"))
 
+iccs <- 
+map_dfr(null_models2, performance::icc, by_group = TRUE) %>% 
+  mutate(model = c(rep("Personality", 3), 
+                   rep("Affect", 3), 
+                   rep("Thought", 3)),
+         ICC = ICC*100)
+
+iccs %>% 
+  ggplot() +
+  geom_col(aes(Group, ICC), fill = "#377eb8") +
+  facet_wrap(~model) +
+  theme_bw()
 ```
@@
 sjPlot::tab_model(SAM1)
-
-## save random effects
-lapply(ranef(SAM1), write.table, 
-       append = TRUE, 
-       file = here::here("data", "raneff from SAM1 for TRT.csv"))
 

### 2022-06-07 manuscript.Rmd
normative and distinctive accuracy

@@
 
-# Results {.tabset .tabset-fade}
+# Results and Discussion {.tabset .tabset-fade}
 
@@
 null_models %>% 
-  kable_style(title = "<center><b>Null Models</b></center>") %>% 
+  kable_style(title = "<center><b>Table 2. Null Models</b></center>") %>% 
   kableExtra::pack_rows("Personality", 1, 5) %>% 
@@
     )
-
-sjPlot::tab_model(null_models2[[1]],
-                  null_models2[[2]],
-                  null_models2[[3]], 
-                  dv.labels = c("Personality", "Affect", "Thought"))
 
@@
 
-In order to decompose the variance in interpersonal accuracy and compare across accuracy measures I ran a series of baseline variance decomposition models on the accuracy measures.
-All analyses were conducted in R’s lme4 package (Bates et al., 2013).
+All analyses were conducted in R’s lme4 package (Bates et al., 2013). The
 
 ```{r}
-# personality
-## final model
-SAM1 <- lmer(ptrait ~ targSRrC + AvgtraitC + 
-                (1 | PerUn) + 
-                (1 | TarUn) + 
-                (1 | DyUn), 
-              data = samdata)
+# for looping purposes
+df_personality_self <- 
+  df_personality %>% 
+  select(perceiver_id:judgment,
+         norm = self_norm,
+         distinct = self_dist)
 
-sjPlot::tab_model(SAM1)
+df_personality_inf <- 
+  df_personality %>% 
+  select(perceiver_id:judgment,
+         norm = inf_norm,
+         distinct = inf_dist)
 
-## extract empirical bayesian estimates for targets
-EBTRTtar <- ranef(SAM1)$TarUn
-EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
-map_dbl(EBTRTtar, sd)
+df_affect <- 
+  df_affect %>% 
+  rename(distinct = self_dist)
 
-## extract empirical bayesian estimates for perceivers
-EBTRTper <- ranef(SAM1)$PerUn
-EBTRTper$PerUn<-as.numeric(row.names(EBTRTper))
-map_dbl(EBTRTper,sd)
+df_list2 <- list(df_personality_self,
+                 df_personality_inf,
+                 df_affect)
 
-## Density plots for random effects will be placed here
+# models
+models_norm_distinct <- 
+  map_dfr(df_list2, ~
 
-## fit a model for each perceiver
-models_dyad <-
-samdata %>%
-  group_by(PerUn) %>%
-  nest() %>%
-  mutate(models = map(data, ~ {
+            lmer(judgment ~ distinct + norm +
+                   (1|perceiver_id) + 
+                   (1|target_id) +
+                   (1|dyad_id),
+                 data = .x) %>%
 
-    lm(ptrait ~ targSRrC + AvgtraitC,
+        broom.mixed::tidy()
+          )
+
+# Accuracy for thoughts is a little different. So, we'll only have two null models for distinctive and normative accuracy for thoughts. See the methods section for details.
+
+models_norm_distinct_thoughts <- 
+  df_thought %>% 
+  rename(Normative = BaselineEA100,
+         Distinctive = CrrctdEAnoneg) %>% 
+  pivot_longer(cols = c(Normative, Distinctive),
+               names_to = "DVs",
+               values_to = "rating") %>% 
+  split(., .$DVs) %>% 
+  map(., ~
+
+        lmer(rating ~ 
+               (1|perceiver_id) + 
+               (1|target_id) +
+               (1|dyad_id),
              data = .x)
 
-  }
         )
-         )
-```
 
-```{r}
-# affect
-samEAC <- lmer (Part ~ targSRrC + NormC + 
-                  (targSRrC + NormC|PerUn) + 
-                  (targSRrC + NormC|TarUn) + 
-                  (targSRrC + NormC|DyUn), 
-                data = samEACaggdata)
+map_dfr(models_norm_distinct_thoughts, isSingular) %>% 
+  kable_style(title = "<center><b>Are the models for thought accuracy singular?</b></center>")
 
-sjPlot::tab_model(samEAC)
+model_norm_thought <- lmer(BaselineEA100 ~ 
+                             (1|perceiver_id),
+                           data = df_thought) %>% broom.mixed::tidy()
+
+model_dist_thought <- lmer(CrrctdEAnoneg ~ 
+                             (1|perceiver_id) + 
+                             (1|target_id) +
+                             (1|dyad_id),
+                           data = df_thought) %>% broom.mixed::tidy()
 
@@
 
+Since the model for normative thought accuracy is singular, we ran the models separately.
+
 ```{r}
-# thought
-# baseline accuracy
-normEASRM<- lmer(BaselineEA100 ~ 
-                   (1|PerUn) + 
-                   (1|TarUn) + 
-                   (1|DyUn) + 
-                   (1|Group), 
-                 data = eaSRMdata)
-
-# corrected for baseline
-diffEASRM<- lmer(CrrctdEAnoneg ~ 
-                    (1|PerUn) + 
-                    (1|TarUn) + 
-                    (1|DyUn) + 
-                    (1|Group), 
-                  data = eaSRMdata)
-
-sjPlot::tab_model(normEASRM, diffEASRM)
+bind_rows(models_norm_distinct,
+          model_norm_thought,
+          model_dist_thought) %>% 
+  kable_style(title = "<center><b>Table 3. Normative and Distinctive Accuracy</b></center>") %>% 
+  kableExtra::pack_rows("Self-reported Personality", 1, 7) %>% 
+  kableExtra::pack_rows("Informant-reported Personality", 8, 14) %>% 
+  kableExtra::pack_rows("Affect", 15, 21) %>% 
+  kableExtra::pack_rows("Normative Thought", 22, 24) %>% 
+  kableExtra::pack_rows("Distinctive Thought", 25, 29)
 ```
@@
 ## Predictors of interpersonal accuracy
-
-WILL WORK ON THIS LATER.
+The last aim of the present study is to test individual-difference predictors of interpersonal accuracy.
+Table 3 demonstrates the relationship between the predictors and interpersonal accuracy across domains.
 
 ```{r}
+df_thought_long <- 
+  df_thought %>% 
+  pivot_longer(cols = InsecAtt_c:rapport_c,
+               names_to = "vars",
+               values_to = "value")
+
+df_thought_long <- split(df_thought2, df_thought2$vars)
+
+models5 <- map_dfr(df_thought5, ~
+            lmer(judgment ~ value +
+             (1 | perceiver_id) + 
+             (1 | target_id) +
+             (1 | dyad_id),
+           data = .x) %>% 
+             broom.mixed::tidy() %>% 
+             suppressWarnings(), 
+           .id = "Predictors"
+           )
+
+df_thought5 <- 
+  df_thought5 %>% 
+  mutate(m1 = map(data, ~
+            lmer(judgment ~ value +
+             (1 | perceiver_id) + 
+             (1 | target_id) +
+             (1 | dyad_id),
+           data = .x)
+                 )
+         )
+
+df_thought3 <- 
+  df_thought %>% 
+  pivot_longer(cols = InsecAtt_c:rapport_c,
+               names_to = "vars",
+               values_to = "value") %>% 
+  group_by(vars) %>% 
+  nest()
+
+df_thought3 <- 
+  df_thought3 %>% 
+  mutate(m1 = map(data, ~
+            lmer(judgment ~ value +
+             (1 | perceiver_id) + 
+             (1 | target_id) +
+             (1 | dyad_id),
+           data = .x)
+                 )
+         )
 
@@
 
-# Discussion
-
 # Author Note

### 2022-06-07 manuscript.Rmd
predictors

@@
 
-```
-
-```{r null models}
+### create a list
 df_list <- list(df_personality,
@@
 
+bind_rows(df_list, .id = "Domain") %>% 
+  mutate(Domain = recode(Domain, 
+                         "1" = "Personality",
+                         "2" = "Affect",
+                         "3" = "Thought")
+         ) %>% 
+  group_by(Domain) %>% 
+  nest() %>% 
+  drop_na() %>% 
+  mutate(N = map_dbl(data, nrow)
+         ) %>% 
+  select(-data) %>% 
+  kable_style(title = "<center><b>Number of Total Observations across Domains</b></center>")
+```
+
+```{r null models}
 null_models <- df_list %>% 
@@
 
-```{r}
-df_thought_long <- 
-  df_thought %>% 
+```{r, include = FALSE}
+# I tried to combine everything in a single loop creating double-nested data but failed miserably
+
+# personality 
+df_personality_long <- 
+  df_personality %>% 
   pivot_longer(cols = InsecAtt_c:rapport_c,
@@
 
-df_thought_long <- split(df_thought2, df_thought2$vars)
+df_personality_long <- split(df_personality_long, df_personality_long$vars)
 
-models5 <- map_dfr(df_thought5, ~
-            lmer(judgment ~ value +
+preds_pers <- map_dfr(df_personality_long, ~
+            lmer(judgment ~ value + self_norm:value + self_dist:value +
+                       (1 | perceiver_id) +
+                       (1 | target_id) +
+                       (1 | dyad_id),                   
+                     data = .x) %>% 
+             broom.mixed::tidy() %>% 
+             suppressWarnings() %>% 
+             suppressMessages(), 
+           .id = "Predictors"
+           )
+
+# affect
+df_affect_long <- 
+  df_affect %>% 
+  pivot_longer(cols = InsecAtt_c:rapport_c,
+               names_to = "vars",
+               values_to = "value")
+
+df_affect_long <- split(df_affect_long, df_affect_long$vars)
+
+preds_aff <- map_dfr(df_affect_long, ~
+            lmer(judgment ~ value + norm:value + distinct:value +
+                       (1 | perceiver_id) +
+                       (1 | target_id) +
+                       (1 | dyad_id),                   
+                     data = .x) %>% 
+             broom.mixed::tidy() %>% 
+             suppressWarnings() %>% 
+             suppressMessages(), 
+           .id = "Predictors"
+           )
+
+# thought
+df_thought_long <- 
+  df_thought %>% 
+  rename(Normative = BaselineEA100,
+         Distinctive = CrrctdEAnoneg) %>% 
+  pivot_longer(cols = InsecAtt_c:rapport_c,
+               names_to = "vars",
+               values_to = "value")
+
+df_thought_long <- split(df_thought_long, df_thought_long$vars)
+
+preds_thou_norm <- map_dfr(df_thought_long, ~
+            lmer(Normative ~ value +
+                       (1 | perceiver_id),
+                     data = .x) %>% 
+             broom.mixed::tidy() %>% 
+             suppressWarnings(), 
+           .id = "Predictors"
+           )
+
+preds_thou_dist <- map_dfr(df_thought_long, ~
+            lmer(Distinctive ~ value +
                        (1 | perceiver_id) + 
@@
            )
+# table 4
+tabl4 <- bind_rows(
+  preds_pers,
+  preds_aff,
+  preds_thou_norm,
+  preds_thou_dist,
+  .id = "Domain"
+) %>% 
+  mutate(across(estimate:df, round, 2),
+         p.value = scales::pvalue(p.value)
+         )
+```
 
-df_thought5 <- 
-  df_thought5 %>% 
-  mutate(m1 = map(data, ~
-            lmer(judgment ~ value +
-             (1 | perceiver_id) + 
-             (1 | target_id) +
-             (1 | dyad_id),
-           data = .x)
-                 )
-         )
-
-df_thought3 <- 
-  df_thought %>% 
-  pivot_longer(cols = InsecAtt_c:rapport_c,
-               names_to = "vars",
-               values_to = "value") %>% 
-  group_by(vars) %>% 
-  nest()
-
-df_thought3 <- 
-  df_thought3 %>% 
-  mutate(m1 = map(data, ~
-            lmer(judgment ~ value +
-             (1 | perceiver_id) + 
-             (1 | target_id) +
-             (1 | dyad_id),
-           data = .x)
-                 )
-         )
-
+```{r}
+tabl4 %>% 
+  select(-Domain) %>% 
+  kable_style(title = "<center><b>Predictors of Interpersonal Accuracy</b></center>") %>% 
+  kableExtra::pack_rows("Personality", 1, 208) %>% 
+  kableExtra::pack_rows("Affect", 209, 416) %>% 
+  kableExtra::pack_rows("Normative Thought", 417, 520) %>% 
+  kableExtra::pack_rows("Distinctive Thought", 521, 676) %>% 
+  kableExtra::scroll_box(height = "1000px")
 ```

### 2022-06-07 manuscript.Rmd
knit!!!1!!one!!

@@
 
+Table 2 represents the null models, and Figure 1 represents the ICCs across domains.
+
 ```{r null models}
@@
   geom_col(aes(Group, ICC), fill = "#377eb8") +
+  labs(title = "Figure 1. ICCs across Domains",
+       x = "") +
   facet_wrap(~model) +
@@
 
-All analyses were conducted in R’s lme4 package (Bates et al., 2013). The
+All analyses were conducted in R’s lme4 package (Bates et al., 2013).
 
@@
 
-Since the model for normative thought accuracy is singular, we ran the models separately.
+Since the model for normative thought accuracy is singular, we ran the models separately. Table 2 represents the normative and distinctive accuracy across domains.
 
